Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-06-01 sec_results.tex
update on results

The two-dimensional associated yield per trigger particle is shown in Figure 1 for pairs of trigger particle and associated particle with 1.0$<\it{p}_{\rm{T, assoc}}<\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{} in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} in the 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class estimated by V0 detector, which covers forward rapidity region. The ridge is clearly seen in high multiplicity class unlike in lower multiplicity classes.

\begin{figure}
	\centering
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr1.pdf} }
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr2.pdf} }
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr3.pdf} }
	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class. The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}. }

\end{figure}

The one-dimensional $\Delta\varphi$ distribution is shown in Figure 2 for pairs of particles with various $\it{p}_{\rm{T}}$ intervals in very high multiplicity class. The associated yield per trigger particle is compared with CMS results. The near-side peak is highest in the 1.0$<\it{p}_{\rm{T}}<$2.0 interval and gradually decreases with increasing $\it{p}_{\rm{T}}$.

The spectra of the ridge yield is shown in Figure 3 in very high multiplicity class and compared with CMS results. The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\it{p}_{\rm{T}}>$0.4 GeV/\it{c}\rm{}. Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%. Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity,, the measurements are can be considered comparable with each other.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals. Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} (left), 2.0$<\it{p}_{\rm{T}}<$3.0 GeV/\it{c}\rm{} (middle) and 3.0$<\it{p}_{\rm{T}}<$4.0 GeV/\it{c}\rm{} (right), respectively. }
	\label{fig:PlotDeltaPhi}
\end{figure}

\begin{figure}
	\centering
	\subfigure{ \includegraphics[width=0.7\textwidth]{./figures/Fig1_RidgeYield.pdf} }
	\caption{(color online) The spectra of ridge yield as function of transverse momentum. The spectrum is compared with CMS result \cite{ridge_pp_1}.}
\end{figure}

@@

To further understand the behavior of the ridge in events including hard processes, the two-dimensional associated yield per trigger particle is measured with the leading track selection as shown in Figure 4. The ridge is still visible in the events where $\it{p}_{\rm{T}}^{\rm{Lead}}>$7 GeV/c, which means that the ridge co-exists with hard-scattering in pp collisions.

>>>>

\subsection{Ridge yield}

Measurement of the correlations function is shown in Fig.~\ref{fig:PlotCorrMBHMT} for 1.0$<\it{p}_{\rm{T, assoc}},\,\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{} in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} in the 0-0.1\% (left), and 0-100\% (right) multiplicity class estimated by V0 detector, which covers forward rapidity region. The ridge is clearly seen in high multiplicity class unlike in lower multiplicity classes.

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr1.pdf} }
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corrmb.pdf} }
	\caption{ Two-dimensional correlations function as function of $\Delta\eta$ and $\Delta\varphi$ in 0-0.1\% (left) and 0-100\% (right) multiplicity class. The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}. }
	\label{fig:PlotCorrMBHMT}
\end{figure}

The one-dimensional $\Delta\varphi$ distribution is shown in Fig.~\ref{fig:PlotDeltaPhi} for pairs of particles with various $\it{p}_{\rm{T}}$ intervals in very high multiplicity class. The associated yield per trigger particle is compared with CMS results. The near-side peak is highest in the 1.0$<\it{p}_{\rm{T}}<$2.0 interval and gradually decreases with increasing $\it{p}_{\rm{T}}$.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals in each multiplicity class. The distributions in upper panels are measured with 0-100\% multiplicity class. The distribution in lower panels are measured with 0-0.1\% multiplicity class. Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} (left), 2.0$<\it{p}_{\rm{T}}<$3.0 GeV/\it{c}\rm{} (middle) and 3.0$<\it{p}_{\rm{T}}<$4.0 GeV/\it{c}\rm{} (right), respectively. }
	\label{fig:PlotDeltaPhi}
\end{figure}

The spectra of the ridge yield are shown in Fig.~\ref{fig:PlotYSpect} in very high multiplicity class and compared with CMS results. The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\it{p}_{\rm{T}}>$0.4 GeV/\it{c}\rm{}. Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%. Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity,, the measurements are can be considered comparable with each other. The spectrum is also compared with model predictions. The PYTHIA8 default and PYTHIA8 + String Shoving are used for the prediction. The PYTHIA8 default is shown as black line and predicts no ridge in pp collisions, which is expected and indicates ignorable jet contamination. The PYTHIA8 + String Shoving is shown as red line and predicts existence of ridge yield in pp collisions, which decreases more rapidly than measurement as transverse momentum increases.

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.7\textwidth]{./figures/Fig1_RidgeYield.pdf} }
	\caption{ The spectra of ridge yield as function of transverse momentum. The filled circles denote the measurement with ALICE and compared with CMS measurement \cite{ridge_pp_1}, which is represented as open box. The two lines show model predictions from PYTHIA8 default(black line) and PYTHIA8 + String Shoving(red line).  }
	\label{fig:PlotYSpect}
\end{figure}

\subsection{Event scale dependent ridge yield}

To further observe the behavior of the ridge yield in events including hard processes,

the two-dimensional associated yield per trigger particle is measured with the leading track selection as shown in Figure 4. The ridge is still visible in the events where $\it{p}_{\rm{T}}^{\rm{Lead}}>$7 GeV/c, which means that the ridge co-exists with hard-scattering in pp collisions.

@@
